### 2007-11-07 pkg/paper/Colorspace/article.Rnw
HLS to HSL in article.Rnw
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/colorspace@26 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

HSV and HLS (and others) because you may have been given a colour in
such a (crappy) colorspace and want to convert it to something
better in order to work with it.  And basically just for completeness!

>>>>

HSV and HSL (and others) because you may have been given a colour in
such a (crappy) colorspace and want to convert it to something
better in order to work with it.  And basically just for completeness!
